\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jim Tran Kelly} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+61 412 561 162 \\ Brisbane, QLD}
\address{\href{mailto:jimkelly.t@outlook.com}{jimkelly.t@outlook.com} \\ \href{https://www.linkedin.com/in/jimkellyt/}{LinkedIn} \\ \href{https://jim-t-kelly.web.app}{https://jim-t-kelly.web.app}} %

\begin{document}

% Education
\begin{rSection}{Education}

{\bf Bachelor of Information Technology (Computer Science)}, Queensland University of Technology\hfill {2020 - 2021}\\
Grade Point Average (GPA): 6.48 / 7.0\\
Transferred from a Bachelor (Honours) of Electrical Engineering (2018 - 2019) to Computer Science. Graduated with distinction.

\end{rSection}

% Skills
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & JavaScript, TypeScript, Golang, HTML, CSS, Python, SQL, Java, C, C++, C\#, Bash, Kotlin\\
 & MATLAB, LaTeX\\
Technologies & Docker, NodeJS, MS SQL, PostgreSQL, Linux, Git, Figma, AWS, GCP, Firebase, Kibana\\
& Ionic, Red Hat OpenShift\\
Frameworks & ReactJS, React-Native, NestJS, AngularJS, gRPC, Camel, Fuse, Tailwind CSS, Sass\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Full-Stack Developer - Consultant} \hfill Jun 2023 - Present\\
Deloitte | Illuminate \hfill \textit{Remote, AU}\\
\textbf{Full-Stack Developer - Graduate} \hfill Nov 2022 - Jun 2023\\
Deloitte | Illuminate \hfill \textit{Melbourne, VIC}
 \begin{itemize}
    \itemsep -3pt {}
    \item Developed a modern web application based supply chain solution using a variety of technologies including TypeScript, Docker, NestJS, Go, Ansible, BullMQ, Redis, SQL, and gRPC.
    \item Built, integrated, and released scalable RESTful APIs connected to data-processing back-end systems.
    \item Analysed and optimised performance bottlenecks in existing back-end data-processing jobs through the implementation of scheduler and worker queues; leading to an average speedup of 2.19 times faster data processing times via concurrency.
    \item Led the development of an integrated Wikidata solution in Go to enable further data enrichment for the application and enhance its functionality.
    \item Created informative and effective documentation, reports, and general comments on all code created.
    \item Demonstrated a strong sense of autonomy and initiative in delivering high-quality software features, troubleshooting complex technical issues, and collaborating with cross-functional teams within an Agile framework, resulting in the successful delivery of the project and positive feedback from stakeholders.
 \end{itemize}

\textbf{Integration Developer - Graduate} \hfill Mar 2022 - Nov 2022\\
Deloitte | Core Business Operations \hfill \textit{Melbourne, VIC}
 \begin{itemize}
    \itemsep -3pt {}
    \item Led the implementation of a Managed File Transfer (MFT) solution and collaborated directly with government clients and stakeholders to build features and resolve issues.
    \item Utilised technologies such as Python, Ansible, GitLab, ElastAlert, Kotlin, Camel, Red Hat OpenShift, and Axway Secure Transport in developing and maintaining the solution across all deployed environments.
    \item Was the primary for and successfully oversaw the go-live release of the MFT solution for a major government client, ensuring a seamless transition with minimal downtime in operation.
    \item Demonstrated strong project management and engineering principles to ensure sustainable delivery of the solution.
 \end{itemize}

\newpage

\textbf{Full-Stack Developer} \hfill Mar 2021 - Mar 2022\\
Digital Purpose \hfill \textit{Brisbane, QLD}
 \begin{itemize}
    \itemsep -3pt {}
    \item Designed, developed, and released web applications for a boutique firm using AngularJS, TypeScript, ThreeJS, and GCP / Firebase.
    \item Constructed APIs and wider tailored technical solutions for web applications to meet client needs.
 \end{itemize}

\textbf{Undergraduate Software Engineer} \hfill Nov 2020 - Mar 2021\\
FutureNet POS \hfill \textit{Brisbane, QLD}
 \begin{itemize}
    \itemsep -3pt {}
    \item Developed a modern point-of-sale (POS) web application using TypeScript, ElectronJS, and IonicJS to replace legacy systems, resulting in improved transaction efficiency, stock-taking, and customer satisfaction.
    \item Utilised Azure cloud computing \& hosting to streamline the application lifecycle.
 \end{itemize}

\end{rSection}

% Projects
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item {I have several projects hosted on GitHub that showcase my dedication to continuously improving my skills as a software engineer, which you can access from my page \href{https://github.com/jamestkelly}{here}. The following are a few of my personal favorites.}
\item \textbf{\href{https://github.com/jamestkelly/personal-portfolio}{Personal Portfolio Website}} {| Designed, programmed, and deployed my own \href{https://jim-t-kelly.web.app}{personal portfolio website} using Figma, Firebase, TypeScript, ThreeJS, React, and Tailwind CSS.}
\item \textbf{\href{https://github.com/jamestkelly/decider}{Decider}} {| This is my most recent project and a work in progress. It is an application I've designed, and developed as a progressive-web-application for coming to a consensus on decisions, complaints and suggestions sharing, and random selection. This application is designed to use a Golang back-end with Firebase Hosting \& Realtime Database alongside Google Cloud Platform, and a React TypeScript front-end with Ionic for mobile application development.}
\item \textbf{\href{https://github.com/jamestkelly/is-my-coffee-cold}{Is My Coffee Cold?}} {| Designed and built a progressive-web-application (PWA) for mobile and desktop using TypeScript, Ionic Capacitor, and Angular. It utilises the WeatherAPI alongside Newton's Rate of Cooling to determine approximately how long you have in any given location before your fresh coffee will go cold.}
\item \textbf{\href{https://github.com/jamestkelly/harold}{Harold}} {| Developed features and am the lead for the Harold chatbot for the \#under30s Deloitte CBO Slack channel. Harold runs as a NodeJS Lambda which is triggered on a Cron Schedule. He uses the groups.info Slack API to retrieve a list of user's for a channel and then sends a question to the channel via a web-hook. The chatbot will ask a randomly selected question to a random user in the channel. This chatbot was built with NodeJS, JavaScript, Severless, and AWS.}
\item \textbf{\href{https://github.com/jamestkelly/K8s-PySpark-Matrix}{K8s PySpark Matrix}} {| Another work in progress, however, a quick proof of concept project to show the capability in replicating the functionality of \href{https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=&cad=rja&uact=8&ved=2ahUKEwiFp-Wipuj_AhVjhVYBHS5kAJQQFnoECA8QAQ&url=https%3A%2F%2Fwww.databricks.com%2F&usg=AOvVaw2NlAEgQTHRQSQHUTnso27O&opi=89978449}{Databricks} for deployment onto on-premises infrastructure. The project is a Python Flask API layer running in Kubernetes on-top of an Apache Spark Kubernetes cluster with scalable scheduler-worker nodes.}

\end{rSection}

\end{document}
